A Bayesian approach to uncertainty in word embedding bias estimation

### 2023-10-20 paper/CLsubmission/bayesBiasCL.tex
final resubmission revisions

In Section \ref{sec:two} we describe the two key measures discussed in
this paper, \textsf{WEAT} and \textsf{MAC}, explaining how they are
calculated and how they are supposed to work. In Section
\ref{sec:challenges} we first argue in Subsection
\ref{subsec:interpretability}, that it is far from clear how results
given in terms of \textsf{WEAT} or \textsf{MAC} are to be interpreted.
Second, in Subsection \ref{subsec:problems} we explain the statistical
problems that arise when one uses pre-averaged data in such contexts, as
these measures do. In Section \ref{sec:bayesian} we explain the
alternative Bayesian approach that we propose. In Section
\ref{sec:results} we elaborate on the results that it leads to,
including low  efficiency of debiasing methods, discussed in Subsection \ref{subsec:rethinking}. Finally, in
Section \ref{sec:related} we spend some time placing our results in the
ongoing discussions.\footnote{\textbf{Disclaimer:} throughout the paper
  we will be mentioning and using word lists and stereotypes we did not
  formulate, which does not mean we condone any judgment made therein or
  underlying a given word selection. For instance, the Gender dataset
  does not recognize non-binary categories, and yet we use it without
  claiming that such categories should be ignored.}$^{, }$ \footnote{A few more philosophical comments on the enterprise of reflecting on bias in language models can be found in Appendix \ref{appendix:philosophical}.}

@@

The underlying intuition is that if a particular harmful stereotype is
learned in a particular embedding, then certain groups of words will be
systematically closer to (or further from) each other. This gives rise
to the idea of protected groups---for example, in guiding online search
completion or recommendation, female words might require protection in
that they should not be systematically closer to stereotypically female
job names, such as ``nurse'', ``librarian'', ``waitress'', and male
words require protection in that they should not be systematically
closer to toxic masculinity stereotypes, such as ``tough'', ``never
complaining'' or ``macho''.\footnote{However, for some research-related
  purposes, such as the study of stereotypes across history \citep{Garg2018years},
  embeddings which do not protect certain classes may also be useful.}

@@

\textsf{WEAT} is inspired by the Implicit Association Test (IAT)
\citep{Nosek2002harvesting} used in psychology, and in some applications it uses almost the
same word sets, allowing for a \emph{prima facie} sensible comparison
with bias in humans. In \citep{Caliskan2017semanticsBiases} the authors argue that significant
biases---thus measured--- similar to the ones discovered by IAT can be
discovered in word embeddings. In \citep{Lauscher2019multidimensional} the methodology is extended
to a multilingual and cross-lingual setting, arguing that using
Euclidean distance instead of cosine similarity does not make much
difference, while the bias effects vary greatly across embedding
models.\footnote{Interestingly, with social media-text trained
  embeddings being less biased than those based on Wikipedia.} A similar
methodology is employed in \citep{Garg2018years}. The authors employ word embeddings
trained on corpora from different decades to study the shifts in various
biases through the century.\footnote{Strictly speaking, these authors
  use Euclidean distances and their differences, but the way they take
  averages and averages thereof is analogous, and so what we will have
  to say about pre-averaging leading to false confidence applies to this
  methodology as well.}

@@

\noindent For each protected word \(t\in T\), and each
attribute set \(A_j\), they first take the mean of distances for this
protected word and all attributes in a given attribute class, and then
take the mean of thus obtained means for all the protected words and all
the protected classes.\footnote{The authors' code is available through
  their github repository at
  \url{https://github.com/TManzini/DebiasMulticlassWordEmbedding}.}

@@

To avoid the problem brought up in this subsection, we employ control
groups and in line with Bayesian methodology, use posterior
distributions and highest posterior density intervals instead of chasing
single-point metrics based on pre-averaged data. Before we do so, we
first explain why pre-averaging and chasing single-number metrics is a
sub-optimal strategy.

@@

Let us illustrate how this problem arises in the context of
\textsf{WEAT}. Once a particular \(s(X,Y,A,B)\) is calculated, the
question arises as to whether a value that high could have arisen by
chance. To address the question, each \(s(X,Y,A,B)\) is used in the
original paper to generate a \(p\)-value by bootstrapping. The
\(p\)-value is the frequency of how often it is the case that
\(s(X_i,Y_i,A,B)>s(X,Y,A,B)\) for sampled equally sized partitions
\(X_i, Y_i\) of \(X\cup Y\). The WEAT score is then computed by
standardizing the difference in means of means by dividing by the
standard deviation of means, see equation \eqref{eq:weat}.

@@

In the bootstrapped samples we would rather expect low \textsf{s} values
and low \textsf{WEAT}: after all, these are just random permutations of
random distances all of which are drawn from the same null distribution. Let's take a look at one such a bootstrapped sample. For the sake of illustration,
 we picked a rather unusual one: the observed test statistic in this sample is 0.39 and 1.27.

@@

	\caption{Bootstrapped distributions of test statistics and effect sizes in a random sample given the null hypothesis. We used a sample from the null  model with N(0,.08) and 16 protected words, and then bootstrapped from it, following the original methodology. One particular bootstrapped sample is highlighted, and discussed further in the text. }
	\label{fig:caliskanCalc}
\end{figure}

@@

In standard Bayesian analysis, the first step is to understand the
data, think hard about the underlying process, and select potential
predictors and the outcome variable. The next step is to formulate a
mathematical description of the generative model of the relationships
between the predictors and the outcome variable. Prior distributions
must then be chosen for the parameters used in the model. Next, Bayesian
inference must be applied to find posterior distributions over the
possible parameter values. Finally, we need to check how well the
posterior predictions reflect the data with a posterior predictive
check. This will be our evaluation of the methods performance, discussed in Subsection \ref{posterior-predictive-check}, and a more complete collection of such results is available in the appendix.

@@

Furthermore, conceptually there are two levels of analysis in our
approach (see Figure \ref{fig:visDag}). On the one hand, we are
interested in the general question of whether related attributes are
systematically closer across the dataset. On the other hand, we are
interested in a more fine-grained picture of the role of the predictor
for particular protected words. Learning in hierarchical Bayesian models
involves using Bayesian inference to update the parameters of the model.
This update is based on the observed data, and estimates are made at
different levels of the data hierarchy. We use hierarchical Bayesian
models in which we simultaneously estimate parameters at the protected
word level and at the global level, assuming that all lower-level
parameters are drawn from global distributions. Such models can be
thought of as incorporating adaptive regularization, which avoids
overfitting and leads to improved estimates for unbalanced datasets.

@@

Now the priors and the hierarchy. We assume all the \(a\) parameters
come from one distribution, that is normal around a higher-level
parameter \(\bar{a}\) and so on for the other three groups of
parameters. That is, \(a_{\mathsf{pw[i]}}\) is the average distance of a
given particular protected word to attributes stereotypically associated
with it, while \(\bar{a}\) is the overall average distance of protected
words to attributes associated with them.\footnote{For a thorough
  introduction to the concepts we're using, see \citep{kruschke2015bayesian,statrethinkingbook2020}.}
\begin{align*}
d_{\mathsf{pw[i]}} \sim \mathsf{Norm}(\bar{d}, \overline{\sigma_d}) &  & 
a_{\mathsf{pw[i]}} \sim \mathsf{Norm}(\bar{a}, \overline{\sigma_a}) \\
h_{\mathsf{pw[i]}} \sim \mathsf{Norm}(\bar{h}, \overline{\sigma_h}) & & 
n_{\mathsf{pw[i]}} \sim \mathsf{Norm}(\bar{n}, \overline{\sigma_n}) 
\end{align*}

@@

\begin{enumerate}
	\item  We come with the same level of agnosticism about how biased a given embedding is with respect to a particular word list, and so we want to use 
	the same priors across all word lists. Prior to the analysis there seem to be no particular reasons to have strong beliefs about the outcomes being different for different word lists. 
	\item We want the priors to provide some level of regularization to avoid over-fitting. Taking coefficient priors centered around zeros is a fairly standard technique equivalent to other machine-learning regularization techniques (see Chapter 6 of \citep{james2013introduction}, especially the section on Bayesian interpretation of ridge regression and the lasso). Hence centering around the no-effect value (in our case, cosine distance equal to 1, or in other words, cosine similarity equal to 0) and non-uniformity.

@@

One useful thing about a Bayesian analysis is that the reader is welcome to re-run it with their own priors, if they find another choice more compelling, which we invite the reader to do.

@@

A posterior predictive check is a technique used to evaluate the fit of
a Bayesian model by comparing its predictions with observed data. The
underlying principle is to generate simulated data from the posterior
distribution of the model parameters and compare them with the observed
data. If the model is a good fit to the data, the simulated data should
resemble the observed data. In Figure \ref{fig:posteriorCheck1} we
illustrate a posterior predictive check for one corpus (Reddit) and one
word list. The remaining posterior predictive checks are in Appendix 
\ref{appendix:posterior}.

@@

In brief, despite one-number metrics suggesting otherwise, our Bayesian
analysis reveals that insofar as the short word lists usually used in
related research projects are involved, there usually are no strong
reasons to claim the presence of systematic bias. Moreover, comparison
between the groups (including control word lists) leads to the
conclusion that the effect sizes (that is, the absolute differences
between cosine distances between groups) tend to be rather small, with
few exceptions. Moreover, the choice of protected words is crucial ---
as there is a lot of variance when it comes to the protected word-level
analysis.

In a bit more detail, the visualizations in Appendix
\ref{appendix:visualizations} show that the situation is more
complicated than merely looking at one-number summaries might suggest.
Note that the axes are sometimes in different scales to increase
visibility.

@@

In general, debiasing might end up leading to lower differences between
general level coefficients for associated and different attributes. But
that usually happens without any major change to the structure of the
coefficients for protected words, sporadic extreme and undesirable
changes for some protected words, usually with the side-effect of
changing what happens with neutral and human predicates.

@@

A worry that one might have is that the original challenge was to develop a single-number bias metric, and that our approach does not reach this goal. Essentially, this is correct: we argue that chasing a single metric is the wrong game to play to start with. In line with general Bayesian methodology, we grant epistemic priority to the inspection of posterior distributions, of which particular single-number summaries are just that. Imperfect summaries that can be easily misinterpreted if no attention is paid to the uncertainties surronding it. Having said this, if one really needs a single-number summary, then mean posterior contrasts between associated and human attributes are closer to adequacy than the single number metrics proposed so  (but they still should come accompanied with some description of the uncertainty involved).

One of our recommendations is that the wordlists should be larger. A possible concern here is that one might ask: \emph{But wouldn't larger wordlists solve the problem with the existing measures of bias?} This is in some sense true: the overconfidence resulting from using aggregated data will be less damaging if more data is used. However, as \citet{Ethayarajh2020Bernstein} prove, the list sizes needed for useful uncertainty estimation from this perspective obtained using theoretical bounds tend to be prohibitive. Bayesian uncertainty estimates, however, scale with size and can be improved and evaluated as the list sizes increase, even if the size improvement is far from the one required by classical theoretical considerations.

@@

\item \citet{Lum2022Debiasing} observe that many group-wise performance meta-metrics used in algorithmic fairness consideration are biased estimators of disparities and propose a double-corrected variance estimator, which provides unbiased estimates and uncertainty quantification of the variance of model performance. This is certaintly valuable. Our approach differs in the following dimensions: it is not clear how bias variance estimator for model performance should be used in the context of group-wise cosine similarity evaluation, where we are not dealing with performance, but with cosine similarities, and where we are not dealing with a binomial distribution. Moreover, while having an unbiased estimate is valuable, if we have one this only means that \emph{in the long run} our estimates would tend to the true value. In the current situation we were looking at, the datasets are relatively small and we want to focus on what can be said before the long run has passed. Moreover, our Bayesian approach allows for regularization, inspection at values levels of granularity, and more straightforward interpretability, as it results in posterior distributions.

@@

\item \citet{zhang2020robustness} shows the limitations of methods that use gender word pairs to detect bias in an embedding space. They claim that using analogies to detect bias may not necessarily reflect societal bias, but rather simply co-occurrence frequency between words. They conduct experiments where they evaluate four popular bias mesures: Direct Bias (DB), Word Association (WA), Neighbourhood Bias Metric (NBM), and Relational Inner Product Association (RIPA). They show that these measures are not robust to changing either the base pair or the form of a word used. This is  a valid point, to some extent related to the limitations on non-contextual models, and to some extent suggesting the inclusion of various word forms in the word list, and not constructing base direction using small word lists. As one of our observations is that the uncertainty resulting from the use of currently existing protected word lists is too large to justify sweeping statements, this is in line with our criticism.

@@

%\newpage

@@

One response to the raising of the issue of bias in natural language
	models might be to say that there is not much point in reflecting on
	such biases, as they are unavoidable. This unavoidability might seem in
	line with the arguments to the effect that learning algorithms are
	always value-laden \citep{JohnsonValueFree}: they employ inductive methods that require
	design-, data-, or risk-related decisions that have to be guided by
	extra-algorithmic considerations. Such choices necessarily involve value
	judgments and have to do, for instance, with what simplifications or
	risks one finds acceptable. Admittedly, algorithmic decision making
	cannot fulfill the value-free ideal, but this only means that even more
	attention needs to be paid to the values underlying different techniques
	and decisions, and to the values being pursued in a particular use of an
	algorithm.

@@

>>>>

In Section \ref{sec:two} we describe the two key measures discussed in
this paper, \textsf{WEAT} and \textsf{MAC}, explaining how they are
calculated and how they are supposed to work. In Section
\ref{sec:challenges} we first argue in Subsection
\ref{subsec:interpretability}, that it is far from clear how results
given in terms of \textsf{WEAT} or \textsf{MAC} are to be interpreted.
Second, in Subsection \ref{subsec:problems} we explain the statistical
problems that arise when one uses pre-averaged data in such contexts, as
these measures do. In Section \ref{sec:bayesian} we explain the
alternative Bayesian approach that we propose. In Section
\ref{sec:results} we elaborate on the results that it leads to,
including low  efficiency of debiasing methods, discussed in Subsection \ref{subsec:rethinking}. Finally, in
Section \ref{sec:related} we spend some time placing our results in the
ongoing discussions. \footnote{\textbf{Disclaimer:} throughout the paper
  we will be mentioning and using word lists and stereotypes we did not
  formulate, which does not mean we condone any judgment made therein or
  underlying a given word selection. For instance, the Gender dataset
  does not recognize non-binary categories, and yet we use it without
  claiming that such categories should be ignored.}$^{, }$ \footnote{A few more philosophical comments on the enterprise of reflecting on bias in language models can be found in Appendix \ref{appendix:philosophical}.}

@@

The underlying intuition is that if a particular harmful stereotype is
learned in a given embedding, then certain groups of words will be
systematically closer to (or further from) each other. This gives rise
to the idea of protected groups---for example, in guiding online search
completion or recommendation, female words might require protection in
that they should not be systematically closer to stereotypically female
job names, such as ``nurse'', ``librarian'', ``waitress'', and male
words require protection in that they should not be systematically
closer to toxic masculinity stereotypes, such as ``tough'', ``never
complaining'' or ``macho''.\footnote{However, for some research-related
  purposes, such as the study of stereotypes across history \citep{Garg2018years},
  embeddings which do not protect certain classes may also be useful.}

@@

\textsf{WEAT} is inspired by the Implicit Association Test (IAT)
\citep{Nosek2002harvesting} used in psychology, and in some applications it uses almost the
same word sets, allowing for a \emph{prima facie} sensible comparison
with bias in humans. In \citep{Caliskan2017semanticsBiases} the authors argue that significant
biases---thus measured--- similar to the ones discovered by IAT can be
found in word embeddings. In \citep{Lauscher2019multidimensional} the methodology is extended
to a multilingual and cross-lingual setting, arguing that using
Euclidean distance instead of cosine similarity does not make much
difference, while the bias effects vary greatly across embedding
models.\footnote{Interestingly, with social media-text trained
  embeddings being less biased than those based on Wikipedia.} A similar
methodology is employed in \citep{Garg2018years}. The authors employ word embeddings
trained on corpora from different decades to study the shifts in various
biases through the century.\footnote{Strictly speaking, these authors
  use Euclidean distances and their differences, but the way they take
  averages and averages thereof is analogous, and so what we will have
  to say about pre-averaging leading to false confidence applies to this
  methodology as well.}

@@

\noindent For each protected word \(t\in T\), and each
attribute set \(A_j\), they first take the mean of distances for this
protected word and all attributes in a given attribute class, and then
take the mean of thus obtained means for all the protected words and all
the protected classes.\footnote{The authors' code is available through
  their GitHub repository at
  \url{https://github.com/TManzini/DebiasMulticlassWordEmbedding}.}

@@

To avoid the problem brought up in this subsection, we employ control
groups and in line with Bayesian methodology, use posterior
distributions and highest posterior density intervals instead of chasing
single-point metrics based on pre-averaged data. Before we do so, we
first explain why pre-averaging and chasing single-number metrics is a
suboptimal strategy.

@@

Let us illustrate how this problem arises in the context of
\textsf{WEAT}. Once a particular \(s(X,Y,A,B)\) is calculated, the
question arises whether a value that high could have arisen by
chance. To address the question, each \(s(X,Y,A,B)\) is used in the
original paper to generate a \(p\)-value by bootstrapping. The
\(p\)-value is the frequency of how often it is the case that
\(s(X_i,Y_i,A,B)>s(X,Y,A,B)\) for sampled equally sized partitions
\(X_i, Y_i\) of \(X\cup Y\). The WEAT score is then computed by
standardizing the difference in means of means by dividing by the
standard deviation of means, see equation \eqref{eq:weat}.

@@

In the bootstrapped samples we would rather expect low \textsf{s} values
and low \textsf{WEAT}: after all, these are just random permutations of
random distances all of which are drawn from the same null distribution. Let's take a look at one such a bootstrapped sample. For the sake of illustration,
 we picked a rather unusual one: the observed test statistic in this sample is $0.39$ and $1.27$.

@@

	\caption{Bootstrapped distributions of test statistics and effect sizes in a random sample given the null hypothesis. We used a sample from the null  model with N($0$, $0.08$) and 16 protected words, and then bootstrapped from it, following the original methodology. One particular bootstrapped sample is highlighted, and discussed further in the text. }
	\label{fig:caliskanCalc}
\end{figure}

@@

In standard Bayesian analysis, the first step is to understand the
data, think hard about the underlying process, and select potential
predictors and the outcome variable. The next step is to formulate a
mathematical description of the generative model of the relationships
between the predictors and the outcome variable. Prior distributions
must then be chosen for the parameters used in the model. Next, Bayesian
inference must be applied to find posterior distributions over the
possible parameter values. Finally, we need to check how well the
posterior predictions reflect the data with a posterior predictive
check. This will be our evaluation of the method's performance, discussed in Subsection \ref{posterior-predictive-check}, and a more complete collection of such results is available in the appendix.

@@

Furthermore, conceptually there are two levels of analysis in our
approach (see Figure \ref{fig:visDag}). On the one hand, we are
interested in the general question of whether related attributes are
systematically closer across the dataset. On the other hand, we are
interested in a more fine-grained picture of the role of the predictor
for particular protected words. Learning in hierarchical Bayesian models
involves using Bayesian inference to update the parameters of the model.
This update is based on the observed data, and estimates are made at
different levels of the data hierarchy. We use hierarchical Bayesian
models in which we simultaneously estimate parameters at the protected
word level and at the global level, assuming that all lower-level
parameters are drawn from global distributions. Such models can be
thought of as incorporating adaptive regularization, which avoids
over-fitting and leads to improved estimates for unbalanced datasets.

@@

Now let's turn to the the priors and the hierarchy. We assume all the \(a\) parameters
come from one distribution, that is normal around a higher-level
parameter \(\bar{a}\) and so on for the other three groups of
parameters. That is, \(a_{\mathsf{pw[i]}}\) is the average distance of a
given particular protected word to attributes stereotypically associated
with it, while \(\bar{a}\) is the overall average distance of protected
words to attributes associated with them.\footnote{For a thorough
  introduction to the concepts we're using, see \citep{kruschke2015bayesian,statrethinkingbook2020}.}
\begin{align*}
d_{\mathsf{pw[i]}} \sim \mathsf{Norm}(\bar{d}, \overline{\sigma_d}) &  & 
a_{\mathsf{pw[i]}} \sim \mathsf{Norm}(\bar{a}, \overline{\sigma_a}) \\
h_{\mathsf{pw[i]}} \sim \mathsf{Norm}(\bar{h}, \overline{\sigma_h}) & & 
n_{\mathsf{pw[i]}} \sim \mathsf{Norm}(\bar{n}, \overline{\sigma_n}) 
\end{align*}

@@

\begin{enumerate}
	\item  We come with the same level of agnosticism about how biased a given embedding is with respect to a particular word list, and so we want to use 
	the same priors across all word lists. Prior to the analysis there seem to be no particular reasons to have strong beliefs about the outcomes being different for different word lists. 
	\item We want the priors to provide some level of regularization to avoid over-fitting. Taking coefficient priors centered around zeros is a fairly standard technique equivalent to other machine-learning regularization techniques (see Chapter 6 of \citep{james2013introduction}, especially the section on Bayesian interpretation of ridge regression and the lasso). Hence, centering around the no-effect value (in our case, cosine distance equal to 1, or in other words, cosine similarity equal to 0) and non-uniformity.

@@

If the reader is concerned about the choice of priors, the publicly available code can be used  to re-run it with their own priors.

@@

A posterior predictive check is a technique used to evaluate the fit of
a Bayesian model by comparing its predictions with observed data. The
underlying principle is to generate simulated data from the posterior
distribution of the model parameters and compare them with the observed
data. If the model is a good fit to the data, the simulated data should
resemble the observed data. In Figure \ref{fig:posteriorCheck1} we
illustrate a posterior predictive check for one corpus (Reddit) and one
word list. The remaining posterior predictive checks are in Appendix 
\ref{appendix:posterior}. The general phenomenon is that the frequency of observed values falling within the 89\% and 55\% highest posterior density predictive intervals are close to these percentages -- which illustrates that our model is not systematically incorrect. Another observation is that the posterior density intervals are relatively wide, which is not unexpected --- this illustrates that information about what treatment/control group a word belongs to is not very useful in predicting its distance to other words, in line with our general methodological comments.

@@

Despite one-number metrics suggesting otherwise, our Bayesian
analysis reveals that insofar as the short word lists usually used in
related research projects are involved, there usually are no strong
reasons to claim the presence of systematic bias. Moreover, comparison
between the groups (including control word lists) leads to the
conclusion that the effect sizes (that is, the absolute differences
between cosine distances between groups) tend to be rather small, with
few exceptions. The choice of protected words is crucial ---
as there is a lot of variance when it comes to the protected word-level
analysis.

One example of a visualization of the results can be found in Figure \ref{fig:empiricalPriorToDebiasing}. First, it illustrates posterior marginal distributions at the top of the model hierarchy, relating  estimated mean cosine distances by groups to each other. Then, it turns to particular protected words and estimates mean cosine distances of attributes to it, also by groups.  Visualizations for other embeddings and word lists can be found in Appendix \ref{appendix:visualizations}. Overall, these show that the situation is more
complicated than merely looking at one-number summaries might suggest.
Note that the axes are sometimes in different scales to increase
visibility.

@@

In general, debiasing might end up leading to lower differences between
general level coefficients for associated and different attributes. But
that usually happens without any major change to the structure of the
coefficients for protected words, sporadic extreme and undesirable
changes for some protected words, usually with the side effect of
changing what happens with neutral and human predicates.

@@

A worry that one might have is that the original challenge was to develop a single-number bias metric, and that our approach does not reach this goal. Essentially, this is correct: we argue that chasing a single metric is the wrong game to play to start with. In line with general Bayesian methodology, we grant epistemic priority to the inspection of posterior distributions, of which particular single-number summaries are just that. Imperfect summaries that can be easily misinterpreted if no attention is paid to the uncertainties surronding it. Having said this, if one really needs a single-number summary, then mean posterior contrasts between associated and human attributes are closer to adequacy than the single number metrics proposed so  (but they still should come accompanied by some description of the uncertainty involved).

One of our recommendations is that the word lists should be larger. A possible concern here is that one might ask: \emph{But wouldn't larger word lists solve the problem with the existing measures of bias?} This is in some sense true: the overconfidence resulting from using aggregated data will be less damaging if more data is used. However, as \citet{Ethayarajh2020Bernstein} prove, the list sizes needed for useful uncertainty estimation from this perspective obtained using theoretical bounds tend to be prohibitive. Bayesian uncertainty estimates, however, scale with size and can be improved and evaluated as the list sizes increase, even if the size improvement is far from the one required by classical theoretical considerations.

@@

\item \citet{Lum2022Debiasing} observe that many group-wise performance meta-metrics used in algorithmic fairness consideration are biased estimators of disparities and propose a double-corrected variance estimator, which provides unbiased estimates and uncertainty quantification of the variance of model performance. This is certaintly valuable. Our approach differs in the following dimensions: it is not clear how bias variance estimator for model performance should be used in the context of group-wise cosine similarity evaluation, where we are not dealing with performance, but with cosine similarities, and where we are not dealing with a binomial distribution. Moreover, while having an unbiased estimate is valuable, if we have one this only means that \emph{in the long run} our estimates would tend to the true value. In the current situation we were looking at, the datasets are relatively small, and we want to focus on what can be said before the long run has passed. Moreover, our Bayesian approach allows for regularization, inspection at values levels of granularity, and more straightforward interpretability, as it results in posterior distributions.

@@

\item \citet{zhang2020robustness} show the limitations of methods that use gender word pairs to detect bias in an embedding space. They claim that using analogies to detect bias may not necessarily reflect societal bias, but rather simply co-occurrence frequency between words. They conduct experiments where they evaluate four popular bias mesures: Direct Bias (DB), Word Association (WA), Neighbourhood Bias Metric (NBM), and Relational Inner Product Association (RIPA). They show that these measures are not robust to changing either the base pair or the form of a word used. This is  a valid point, to some extent related to the limitations on non-contextual models, and to some extent suggesting the inclusion of various word forms in the word list, and not constructing base direction using small word lists. As one of our observations is that the uncertainty resulting from the use of currently existing protected word lists is too large to justify sweeping statements, this is in line with our criticism.

@@

\newpage

@@

One response to the raising of the issue of bias in natural language
	models might be to say that there is not much point in reflecting on
	such biases, as they are unavoidable. This unavoidability might seem in
	line with the arguments to the effect that learning algorithms are
	always value-laden \citep{JohnsonValueFree}: they employ inductive methods that require
	design-, data-, or risk-related decisions that have to be guided by
	extra-algorithmic considerations. Such choices necessarily involve value
	judgments and have to do, for instance, with what simplifications or
	risks one finds acceptable. Admittedly, algorithmic decision-making
	cannot fulfill the value-free ideal, but this only means that even more
	attention needs to be paid to the values underlying different techniques
	and decisions, and to the values being pursued in a particular use of an
	algorithm.

@@

%\pagebreak
